\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=1.2cm]{geometry}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[default]{raleway}
\usepackage{fontawesome5}
\usepackage{fancyhdr}
\usepackage{tikz}

% Color definitions
\definecolor{darkblue}{RGB}{31, 78, 121}
\definecolor{accentgreen}{RGB}{76, 175, 80}
\definecolor{lightgray}{RGB}{245, 245, 245}
\definecolor{mediumgray}{RGB}{200, 200, 200}

% PDF metadata
\hypersetup{colorlinks=true, linkcolor=darkblue, urlcolor=darkblue}

% Remove page numbers
\pagestyle{empty}

% Custom commands with improved design
\newcommand{\sectiontitle}[1]{%
    \vspace{10pt}
    {\Large\bfseries\color{darkblue}#1}
    \nopagebreak
    \vspace{6pt}
    {\color{accentgreen}\hrule height 2pt}
    \vspace{8pt}
}

\newcommand{\jobtitle}[5]{%
    \textbf{#1} \hfill \textit{\small #2}\\
    {\color{darkblue}\textit{#3}} \hfill {\small #4}\\
    \textit{#5}\\[8pt]
}

\newcommand{\degreeline}[4]{%
    \textbf{#1} \hfill \textit{\small #2}\\
    {\small #3} \hfill {\color{darkblue}\textbf{#4}}\\[3pt]
}

\setlist[itemize]{leftmargin=0.5cm, itemsep=1pt, parsep=0pt}

\begin{document}

% Header with improved spacing
\begin{center}
    {\fontsize{32}{36}\selectfont\bfseries\color{darkblue}Marc Schneider}
    
    {\large Research Associate | Aerospace Engineering}
    \\
    % {\normalsize\color{accentgreen}Guided Missiles, Guidance Laws \& Navigation Systems}
    {\normalsize\color{accentgreen}Guidance, Navigation \& Control | Machine Learning \& Sensor Fusion}
    
    \vspace{10pt}
    
    {\small
    \faPhone\ +49 160 2421697 \quad \faEnvelope\ \href{mailto:marc@marc-schneider.de}{marc@marc-schneider.de} \quad \faMapMarker\ Stuttgart, Germany
    
    \vspace{4pt}
    
    \faLinkedinIn\ \href{https://www.linkedin.com/in/marc-schneider-96a8a3238/}{LinkedIn} \quad \faResearchgate\ \href{https://www.researchgate.net/profile/Marc-Schneider-23}{ResearchGate}
    }
\end{center}

{\color{mediumgray}\hrule height 1pt}

\vspace{2pt}

% Professional Summary
\sectiontitle{Professional Summary}
Aerospace engineer with proven expertise in managing independent research projects from conception to completion. Skilled educator with experience teaching seminars and supervising students at all levels. Specialized in guidance systems, machine learning, sensor fusion, and control theory with focus on trajectory prediction, missile guidance, and autonomous systems. Strong background in mathematical modeling, simulation, and algorithm development.

\vspace{6pt}

% Work Experience
\sectiontitle{Work Experience}

\jobtitle{Research Associate}{Aug. 2020 -- July 2026}{Institute of Flight Mechanics and Controls, University of Stuttgart}{Stuttgart, Germany}{Overall topic: Guidance and navigation for guided missiles}
% \hspace{1em}\textbf{Research Focus:} 

\vspace{-9pt}

\hspace{-0.0em}\textbf{Projects:}
\begin{itemize}[leftmargin=1.0cm]
    \item \textbf{Machine Learning for Cooperative Guided Missiles} -- Stochastic trajectory prediction using normalizing flows

    \item \textbf{Sensor-based Reinforcement Learning} -- Autonomous emergency landing on low-gravity celestial bodies

    \item \textbf{Sensor Fusion for Guided Missile Navigation} -- Multi-sensor integration (IMU, GNSS, Radar, IR) with delayed measurements

    \item \textbf{Multi-Hypothesis Guidance} -- Guidance command computation under uncertain target maneuvers
\end{itemize}

\hspace{0.0em}\textbf{Teaching \& Course Development:}
\begin{itemize}[leftmargin=1.0cm]
    \item \textbf{Estimation Techniques Seminar} (Schätzverfahren-Seminar) -- Course instructor and content developer (every semester since 2021)
    \item \textbf{Aerobotics Seminar} -- Instructor and curriculum developer (2021--2024), supervising Reinforcement Learning and Model Predictive Control topics
    \item \textbf{Student Supervision:} Mentored 7 master's theses and 1 bachelor's thesis with focus on advanced ML and control theory topics
\end{itemize}

\vspace{5pt}

\jobtitle{Research Assistant}{Sep. 2018 -- Nov. 2018}{Institute of Flight Mechanics and Controls, University of Stuttgart}{Stuttgart, Germany}{Further development of DA40 flight simulator and implementation of helicopter simulation model.}

\jobtitle{Research Assistant}{May 2018 -- Aug. 2018}{Institute of Flight Mechanics and Controls, University of Stuttgart}{Stuttgart, Germany}{Tutor for "Flugregelungsentwurf" course: Flight simulator enhancement and support for student projects.}

\jobtitle{Intern}{Apr. 2017 -- Aug. 2017}{MAHLE GmbH}{Stuttgart, Germany}{Thermal management system design for Lithium-Ion batteries. Analysis and optimization of cooling systems.}

\jobtitle{Intern}{Jun. 2014 -- Aug. 2014}{ZENTNER Elektrik-Mechanik GmbH}{Freiburg, Germany}{Introductory internship: Metal processing, machining, and basic mechanical engineering principles.}

% \vspace{5pt}

% Education
\sectiontitle{Education}

\degreeline{Master's Thesis}{2019 -- 2020}{Path planning and obstacle avoidance for multiple UAVs using POMDP \hfill \textit{Grade: 1.0}}{Queensland University of Technology, Brisbane, Australia}

\degreeline{Master of Science in Aerospace Engineering}{2018 -- 2020}{GPA: 1.3}{University of Stuttgart}

\degreeline{Bachelor of Science in Aerospace Engineering}{2014 -- 2018}{GPA: 1.7}{University of Stuttgart}

\degreeline{High School Diploma (Abitur)}{2006 -- 2014}{GPA: 1.0}{Kepler Gymnasium Freiburg}

\vspace{15pt}


% Skills
\sectiontitle{Technical Skills \& Core Competencies}

\textbf{Research \& Development:} Machine Learning, Hyperparameter Tuning, Algorithms, Simulations, Kalman Filtering, Guidance Laws, Control Theory, Estimation Theory, Sensor Fusion, Flight Mechanics, Multi-Agent Systems

\vspace{6pt}

\textbf{Programming Languages:}
\begin{itemize}
    \item \textbf{Expert:} Python (PyTorch, NumPy, SciPy), MATLAB, Simulink
    \item \textbf{Advanced:} \LaTeX, Git, Bash
    \item \textbf{Intermediate:} C/C++
\end{itemize}

\vspace{6pt}

\textbf{Languages:}
\begin{itemize}
    \item German (C2 -- Native Speaker)
    \item English (C1 -- Fluent)
    \item French (B1 -- Intermediate)
\end{itemize}

\vspace{6pt}

\textbf{Tools \& Frameworks:} GitHub Copilot, Deep Learning Frameworks, Version Control Systems, Containerization

\vspace{15pt}

% Supervised Theses
\sectiontitle{Supervised Theses}

\begin{enumerate}[label=\textbf{[\arabic*]}, leftmargin=0.8cm, itemsep=3pt]
    \item (2025) \textit{Stochastic Trajectory Prediction of Civil Aircraft using Conditional Normalizing Flows} -- Master's Thesis
    \item (2025) \textit{Development and Implementation of a GPS Monitoring Algorithm} -- Master's Thesis
    \item (2024) \textit{Reachability Prediction Using Neural Networks} -- Master's Thesis (paper pending)
    \item (2023) \textit{Reinforcement Learning-Based Missile Evasion Strategies} -- Master's Thesis
    \item (2022) \textit{Sensor Fusion for Distributed Directional Measurements} -- Master's Thesis
    \item (2022) \textit{Predictive Guidance Law Considering Induced Drag} -- Bachelor's Thesis
    \item (2021) \textit{Model Predictive Control Guidance Law for Guided Missiles} -- Master's Thesis
\end{enumerate}

\vspace{15pt}



% new page
\newpage
% Publications
\sectiontitle{Publications}

\begin{enumerate}[label=\textbf{[\arabic*]}, leftmargin=0.8cm, itemsep=3pt]
    \item (2025). "Many-vs-Many Missile Guidance via Virtual Targets" (preprint). \href{https://arxiv.org/abs/2511.02526}{arXiv}
    
    \item (2025). "Autonomous Evasive Maneuvers Against Missiles Through Reinforcement Learning." \href{https://www.researchgate.net/publication/387995943_Autonomous_Evasive_Maneuvers_against_Missiles_through_Reinforcement_Learning}{ResearchGate}
    
    \item (2025). "Real-Time Cooperative Target Allocation for Guided Missiles: Leveraging Optimal Control and Multiple Trajectories." \href{https://arc.aiaa.org/doi/10.2514/6.2025-1907}{AIAA}
    
    \item (2025). "Virtual Target Trajectory Prediction for Stochastic Targets." \href{https://arxiv.org/pdf/2504.01851}{arXiv}
    
    \item (2024). "Trajectory Prediction for Missile Targets: A Probabilistic Approach Using Machine Learning." \href{https://www.researchgate.net/publication/381520100_Trajectory_Prediction_for_Missile_Targets_A_Probabilistic_Approach_Using_Machine_Learning}{ResearchGate}
    
    \item (2023). "Radar-Aided Inertial Navigation with Delayed Measurements." \href{https://www.researchgate.net/publication/360484762_Radar-Aided_Inertial_Navigation_with_Delayed_Measurements}{ResearchGate}
    
    \item (2023). "Enhancing Target Acquisition in Long-Range Missiles through Multi-Sensor Fusion." \href{https://www.researchgate.net/publication/377395801_Enhancing_Target_Acquisition_in_Long-Range_Missiles_through_Multi-Sensor_Fusion}{ResearchGate}
    
    \item (2022). "Multi-Hypothesis Guidance With Interacting Multiple Model Filter." \href{https://www.researchgate.net/publication/357595202_Multi-Hypothesis_Guidance_With_Interacting_Multiple_Model_Filter}{ResearchGate}
\end{enumerate}

\vspace{15pt}

\vfill

\begin{center}
    \small
    \textit{Stuttgart, January 3, 2026}
\end{center}

\end{document}
